### 2024-10-31 conference_101719.tex
init commit

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Conference Paper Title HAWAII*\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
}

\maketitle

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2024-10-31 paper.tex
finished until proposed method / problem formulation

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Multi-Task Temporal and Spatial Networks for High-Precision Event Spotting in Volleyball Videos\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Hoang Quoc Nguyen}
\IEEEauthorblockA{\textit{AI Robotics} \\
\textit{University of Science and Technology}\\
Daejeon, 34113, Republic of Korea \\
nqhoang@ust.ac.kr}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
}

\maketitle

\begin{abstract}
    Understanding the precise timing and location of events is crucial for analyzing sports videos, especially in fast-paced sports like volleyball. We introduce a new task: high-precision spatial-temporal event spotting, which aims to detect both when and where key actions occur. To support this, we present the KOVO Volleyball Event Dataset, featuring 947 rally videos, and 5,935 events, annotated for both temporal and spatial localization. Our best model achieves a combined mAP of 85.46 across various temporal and spatial thresholds. Notably, we find that incorporating spatial predictions enhances temporal mAP by 5.89 points, underscoring the synergy between spatial and temporal analysis. To the best of our knowledge, this is the first work addressing this task, establishing a strong baseline for future research in spatial-temporal event spotting.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}

Video understanding has emerged as a cornerstone in computer vision, offering valuable insights into dynamic scenes for applications such as sports analytics, surveillance, and autonomous systems. This field encompasses various tasks designed to interpret and analyze actions over time. Among these, \textit{Video Classification} aims to assign a single label to an entire video, providing a broad understanding of the content but often lacking frame-level precision. In contrast, \textit{Temporal Action Localization (TAL)} focuses on identifying time intervals where specific actions occur within untrimmed videos. Complementing these is \textit{Precise Action Spotting (PES)}, which identifies the precise frames that capture key events, requiring models to discern subtle temporal differences and distinguish visually similar frames \cite{spot22}.

Recent advancements in action spotting, such as \textit{T-DEED} \cite{tdeed23} and \textit{E2E-Spot} \cite{spot22}, have demonstrated the ability of models to achieve frame-level precision in fast-paced events using deep learning architectures. Datasets like \textit{FigureSkating} \cite{figureskating} and \textit{FineDiving} \cite{finediving} have been pivotal in advancing action spotting, emphasizing the importance of precise temporal detection in sports with individual athletes. However, these datasets are tailored to specific sports and do not capture the complexity and rapid dynamics of team-based, high-speed sports, such as volleyball.

In volleyball, rapid play transitions occur within specific areas of the court, making precise spatial localization as important as temporal accuracy. To address this, we introduce the new task of \textit{high-precision spatial-temporal event spotting}, designed to detect both the exact timing and spatial location of key events. Unlike conventional action spotting, this task provides richer insights into player positioning and movement patterns, which are crucial for analyzing volleyball gameplay.

In other sports, datasets like \textit{SoccerNet-v2} \cite{soccernetv2} have pushed the boundaries of action spotting through rich temporal and spatial annotations, significantly advancing model capabilities. Yet, no equivalent dataset exists for volleyball, a sport characterized by its rapid exchanges and the need for precise localization of actions. To fill this gap, we introduce the \textit{KOVO Event Dataset}, comprising 947 rally videos, 890,797 frames, and 5,935 annotated key actions. This dataset offers granular annotations for both temporal and spatial event localization, making it a valuable resource for developing models that capture the intricacies of volleyball.

Our contributions are threefold:
\begin{itemize}
    \item \textbf{New Task Introduction:} We introduce the task of high-precision spatial-temporal event spotting, specifically tailored for the dynamics of volleyball.
    \item \textbf{Dataset Development:} We present the \textit{KOVO Event Dataset}, the first of its kind to include detailed temporal and spatial annotations for volleyball rallies, aimed at fostering research in this area.
    \item \textbf{Model Development:} We propose a multi-task deep learning model that jointly predicts event timing and spatial positions, leveraging this dual focus to achieve improved performance. Notably, incorporating spatial predictions into our model enhances temporal mAP by 5.89 points.
\end{itemize}

Our best model achieves a temporal mAP of 90.59, a spatial mAP of 77.94, and a combined mAP of 85.46, providing a strong baseline for this new task. To the best of our knowledge, this work is the first to explore high-precision spatial-temporal event spotting in volleyball, setting the stage for future research in this area.

% TODO: Fill this when finish paper
% The paper proceeds with a discussion of related work in Section 2, a detailed description of our approach in Section 3, the experimental setup in Section 4, results in Section 5, and conclusions in Section 6.

\section{Related work}

\subsection{Video Classification}

Video classification aims to predict a single label for an entire video, in contrast to event spotting, which requires precise frame-level labeling. This distinction introduces unique challenges: video classification can leverage sparse frame sampling \cite{tsn}, whereas event spotting demands dense sampling to capture rapid changes in events. Additionally, classification models often employ global space-time pooling \cite{8578773} or temporal consensus \cite{zhou2018temporalrelationalreasoningvideos} to produce video-level predictions, while event spotting necessitates preserving high temporal resolution.

\subsection{Temporal Action Localization}

Temporal Action Localization (TAL) aims to identify the time intervals when specific actions occur in untrimmed videos, making it ideal for longer actions that are not instantaneous. Unlike video classification, which assigns a single label to an entire video, TAL requires precise start and end times, making it more complex.

TAL methods are typically categorized into two groups: two-stage \cite{9578330,10.1007/978-3-319-46487-9_47} and one-stage \cite{10203543,zhang2022actionformer} approaches. Two-stage models generate action proposals before classifying them, while one-stage models directly predict actions and their intervals in a streamlined process. Recent methods, like ActionFormer \cite{zhang2022actionformer} and TriDet \cite{tridet}, leverage advanced architectures, including transformers and feature pyramids, to improve temporal precision across varying action durations. Anchor-free approaches \cite{9171561} have further enhanced flexibility in predicting actions without relying on predefined time windows.

TAL's development has been driven by extensive datasets and benchmarks such as ActivityNet \cite{ActivityNet}, EPIC-KITCHENS \cite{damen2018scalingegocentricvisionepickitchens}, and THUMOS Challenge \cite{Idrees_2017}, making it a well-explored field for understanding complex, prolonged actions in videos. However, it remains distinct from action spotting, which focuses on identifying brief, precise moments in fast-paced scenarios.

\subsection{Precise Event Spotting (PES)}\label{AA}

Precise Event Spotting (PES) aims to detect the exact frames of key events in untrimmed videos, making it ideal for fast, critical moments in sports. Unlike Temporal Action Localization (TAL), which spans broader time intervals, PES requires frame-level accuracy, crucial for detailed sports analysis where slight timing shifts can alter game interpretations.

Datasets like \textit{FigureSkating} \cite{figureskating} and \textit{FineDiving} \cite{finediving} have advanced PES with frame-level annotations, but focus on simpler, individual sports. Recent methods, such as \textit{T-DEED} \cite{tdeed23} and \textit{E2E-Spot} \cite{spot22}, enhance precision by refining temporal representations and avoiding pooling, but lack spatial context needed for team sports.

In volleyball, spatial localization is as critical as timing. Understanding event locations is key to analyzing player movements and strategies. Our work addresses this by introducing a new task and dataset for high-precision spatial-temporal event spotting in volleyball, capturing both event timing and location.

Inspired by \textit{E2E-Spot} \cite{spot22}, our approach uses RegNet-Y \cite{radosavovic2020designingnetworkdesignspaces} with GSM \cite{9156729} for adaptive temporal shifts. This combination balances efficiency and precision, making it ideal for capturing complex spatial-temporal dynamics in volleyball.

\section{Dataset Overview}

\subsection{Data Content and Statistics}
\subsection{Annotation Process}
\subsection{Dataset Splits}
\subsection{Release and Access}
Due to the large size of the dataset, we are unable to release the full-resolution (1280x720) videos in this paper. However, we have made a resized version (512x288 resolution) along with the corresponding annotations available on Kaggle, totaling 100GB. The dataset can be accessed at \url{www.kaggle.com/soon}.

\section{PROPOSED METHOD}
\subsection{Problem Formulation}
\textbf{Spatial-Temporal Event Spotting (STES)} aims to identify both the precise time and location of events within untrimmed videos. Given a video with \(N\) frames \(x_1, \ldots, x_N\) and a set of \(K\) event classes \(c_1, \ldots, c_K\), the goal is to predict a sparse set of frame indices where events occur, as well as the corresponding event class and spatial coordinates. Each prediction is represented as \((t, c_t, s_t)\), where \(t\) is the frame index, \(c_t\) is the predicted event class, and \(s_t\) is the spatial location of the event within that frame. A temporal prediction is considered correct if it falls within a small temporal tolerance \(\sigma_f\) frames of the labeled event and matches the ground-truth class. Similarly, spatial predictions are deemed correct if the distance between the predicted location \(s_t\) and the ground-truth event location is within a specified threshold \(\sigma_p\). For STES, these tolerances are kept small, requiring precise frame-level accuracy, and it assumes that videos are captured with sufficiently high frame rates.

To perform well on this task, several key requirements must be met:
\begin{itemize}
    \item \textbf{Local Spatial-Temporal Features}: The model should capture subtle visual changes and movements across neighboring frames, essential for distinguishing between similar-looking moments.
    \item \textbf{Long-Term Temporal Context}: A broader temporal window allows the model to understand events in context, such as how player positions or actions evolve before and after a critical moment.
    \item \textbf{Dense Per-Frame Predictions}: For each frame \(x_t\), the model produces a prediction \((\hat{y}_t, \hat{s}_t)\), where \(\hat{y}_t \in \mathbb{R}^K\) is a vector of logits representing class probabilities, and \(\hat{s}_t \in \mathbb{R}^2\) represents the \(x, y\) coordinates of the event within the frame. The final class \(c_t\) is obtained by applying argmax to \(\hat{y}_t\), ensuring frame-level precision for each event.
\end{itemize}

These requirements call for a robust and end-to-end trainable architecture capable of leveraging both temporal and spatial information. Our approach utilizes a sequence model that integrates local spatial-temporal features.

\subsection{Model Architecture}
\subsubsection{Feature Extractor}
\subsubsection{Temporal Event Detection}
\subsubsection{Spatial Event Detection}
\subsubsection{Multi-Task Learning}
\subsubsection{Loss Function}

\section{EXPERIMENTS}
\label{sec:experiments}
\subsection{Implementation Details}
\subsection{Training Strategy}
\subsection{Evaluation Metrics}

\section{CONCLUSIONS}
\section*{Acknowledgment}

\bibliographystyle{IEEEtran}
\bibliography{references}
\end{document}

### 2024-10-31 paper.tex
refine abstract for clarity and consistency in terminology

@@
 \begin{abstract}
-    Understanding the precise timing and location of events is crucial for analyzing sports videos, especially in fast-paced sports like volleyball.
-We introduce a new task: high-precision spatial-temporal event spotting, which aims to detect both when and where key actions occur.
-To support this, we present the KOVO Volleyball Event Dataset, featuring 947 rally videos, and 5,935 events, annotated for both temporal and spatial localization.
+    In sport videos analysis, especially in speedy sports such as Volleyball, understanding and localizing the precise timing and location of actions and events are critical.
+We introduce a new task: precise spatio-temporal event spotting, which aims to detect both when and where key events happen.
+To support this, we develop the KOVO Volleyball Event Dataset, featuring 947 rally videos, and 5,935 events, annotated for both temporal and spatial localization.
 Our best model achieves a combined mAP of 85.46 across various temporal and spatial thresholds.
 Notably, we find that incorporating spatial predictions enhances temporal mAP by 5.89 points, underscoring the synergy between spatial and temporal analysis.
-To the best of our knowledge, this is the first work addressing this task, establishing a strong baseline for future research in spatial-temporal event spotting.
+To the best of our knowledge, this is the first work addressing this task, establishing a strong baseline for future research in spatio-temporal event spotting.
 \end{abstract}

### 2024-10-31 paper.tex
rewording

@@
 
-\title{Multi-Task Temporal and Spatial Networks for High-Precision Event Spotting in Volleyball Videos\\
-{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
-should not be used}
+\title{Multi-Task Temporal and Spatial Networks for Precise Event Spotting in Volleyball Videos\\
 \thanks{Identify applicable funding agency here. If none, delete this.}
@@
 \begin{IEEEkeywords}
-component, formatting, style, styling, insert
+precise event spotting, video understanding, spatial temporal event spotting, deep learning, volleyball, sport
 \end{IEEEkeywords}
@@
 In volleyball, rapid play transitions occur within specific areas of the court, making precise spatial localization as important as temporal accuracy.
-To address this, we introduce the new task of \textit{high-precision spatial-temporal event spotting}, designed to detect both the exact timing and spatial location of key events.
+To address this, we introduce the new task of \textit{Precise spatio-temporal event spotting}, designed to detect both the exact timing and spatial location of key events.
 Unlike conventional action spotting, this task provides richer insights into player positioning and movement patterns, which are crucial for analyzing volleyball gameplay.
@@
 \begin{itemize}
-    \item \textbf{New Task Introduction:} We introduce the task of high-precision spatial-temporal event spotting, specifically tailored for the dynamics of volleyball.
+    \item \textbf{New Task Introduction:} We introduce the task of Precise spatio-temporal event spotting, specifically tailored for the dynamics of volleyball.
     \item \textbf{Dataset Development:} We present the \textit{KOVO Event Dataset}, the first of its kind to include detailed temporal and spatial annotations for volleyball rallies, aimed at fostering research in this area.
@@
 Our best model achieves a temporal mAP of 90.59, a spatial mAP of 77.94, and a combined mAP of 85.46, providing a strong baseline for this new task.
-To the best of our knowledge, this work is the first to explore high-precision spatial-temporal event spotting in volleyball, setting the stage for future research in this area.
+As far as we are aware, this work is the first to explore Precise spatio-temporal event spotting in volleyball, setting the stage for future research in this area.
 
@@
 
-Temporal Action Localization (TAL) aims to identify the time intervals when specific actions occur in untrimmed videos, making it ideal for longer actions that are not instantaneous.
-Unlike video classification, which assigns a single label to an entire video, TAL requires precise start and end times, making it more complex.
+The goal of Temporal Action Localization (TAL) is to localize the temporal intervals when specific actions occur in untrimmed videos, making it ideal for prolonged actions that are not instantaneous.
+In contrast to video classification, which assigns a single label to an entire video, TAL requires precise start and end times, adding more complexity.
 
-TAL methods are typically categorized into two groups: two-stage \cite{9578330,10.1007/978-3-319-46487-9_47} and one-stage \cite{10203543,zhang2022actionformer} approaches.
-Two-stage models generate action proposals before classifying them, while one-stage models directly predict actions and their intervals in a streamlined process.
-Recent methods, like ActionFormer \cite{zhang2022actionformer} and TriDet \cite{tridet}, leverage advanced architectures, including transformers and feature pyramids, to improve temporal precision across varying action durations.
+Typically, there are two approaches to TAL: two-stage \cite{9578330,10.1007/978-3-319-46487-9_47} and one-stage \cite{10203543,zhang2022actionformer}.
+In two-stage models, action proposals are generated first then used for classification, while action class and temporal intervals are done in one streamlined process.
+Recently, advanced techniques such as Transformers and Feature Pyramid Network are incorporated to improve temporal precision across varying action duractions, like ActionFormer \cite{zhang2022actionformer} and TriDet \cite{tridet}.
 Anchor-free approaches \cite{9171561} have further enhanced flexibility in predicting actions without relying on predefined time windows.
 
-TAL's development has been driven by extensive datasets and benchmarks such as ActivityNet \cite{ActivityNet}, EPIC-KITCHENS \cite{damen2018scalingegocentricvisionepickitchens}, and THUMOS Challenge \cite{Idrees_2017}, making it a well-explored field for understanding complex, prolonged actions in videos.
-However, it remains distinct from action spotting, which focuses on identifying brief, precise moments in fast-paced scenarios.
+Datasets and benchmarks such as ActivityNet \cite{ActivityNet}, EPIC-KITCHENS \cite{damen2018scalingegocentricvisionepickitchens}, and THUMOS Challenge \cite{Idrees_2017} have driven the development of TAL, which has become a central topic in Video Understand.
+By contrast, the precise identification of single-timestamp events remains less explored.
 
-\subsection{Precise Event Spotting (PES)}\label{AA}
+\subsection{Precise Event Spotting (PES)}
 
@@
 Understanding event locations is key to analyzing player movements and strategies.
-Our work addresses this by introducing a new task and dataset for high-precision spatial-temporal event spotting in volleyball, capturing both event timing and location.
+Our work addresses this by introducing a new task and dataset for Precise spatio-temporal event spotting in volleyball, capturing both event timing and location.
 
 Inspired by \textit{E2E-Spot} \cite{spot22}, our approach uses RegNet-Y \cite{radosavovic2020designingnetworkdesignspaces} with GSM \cite{9156729} for adaptive temporal shifts.
-This combination balances efficiency and precision, making it ideal for capturing complex spatial-temporal dynamics in volleyball.
+This combination balances efficiency and precision, making it ideal for capturing complex spatio-temporal dynamics in volleyball.
 
@@
 \subsection{Release and Access}
-Due to the large size of the dataset, we are unable to release the full-resolution (1280x720) videos in this paper.
+Given the large size of the dataset, we are unable to release the full-resolution (1280x720) videos in this paper.
 However, we have made a resized version (512x288 resolution) along with the corresponding annotations available on Kaggle, totaling 100GB.
@@
 
-\section{PROPOSED METHOD}
+\section{Proposed Method}
 \subsection{Problem Formulation}
-\textbf{Spatial-Temporal Event Spotting (STES)} aims to identify both the precise time and location of events within untrimmed videos.
-Given a video with \(N\) frames \(x_1, \ldots, x_N\) and a set of \(K\) event classes \(c_1, \ldots, c_K\), the goal is to predict a sparse set of frame indices where events occur, as well as the corresponding event class and spatial coordinates.
+\textbf{Precise Spatio-Temporal Event Spotting (PSTES)} aims to identify both the precise time and location of events within untrimmed videos.
+For a sequence of \(N\) frames \(x_1, \ldots, x_N\) and a set of \(K\) event classes \(c_1, \ldots, c_K\), the goal is to predict a sparse set of frame indices where events occur, as well as the corresponding event class and spatial coordinates.
 Each prediction is represented as \((t, c_t, s_t)\), where \(t\) is the frame index, \(c_t\) is the predicted event class, and \(s_t\) is the spatial location of the event within that frame.
-A temporal prediction is considered correct if it falls within a small temporal tolerance \(\sigma_f\) frames of the labeled event and matches the ground-truth class.
+A temporal prediction is deemed correct if it falls within a small temporal tolerance \(\sigma_f\) frames of the labeled event and matches the ground-truth class.
 Similarly, spatial predictions are deemed correct if the distance between the predicted location \(s_t\) and the ground-truth event location is within a specified threshold \(\sigma_p\).
-For STES, these tolerances are kept small, requiring precise frame-level accuracy, and it assumes that videos are captured with sufficiently high frame rates.
+For PSTES, these tolerances are kept small, requiring precise frame-level accuracy, and it assumes that videos are captured with sufficiently high frame rates.
 
-To perform well on this task, several key requirements must be met:
+To achieve strong performance on this task, several important factors must be considered:
+
 \begin{itemize}
-    \item \textbf{Local Spatial-Temporal Features}: The model should capture subtle visual changes and movements across neighboring frames, essential for distinguishing between similar-looking moments.
-    \item \textbf{Long-Term Temporal Context}: A broader temporal window allows the model to understand events in context, such as how player positions or actions evolve before and after a critical moment.
-    \item \textbf{Dense Per-Frame Predictions}: For each frame \(x_t\), the model produces a prediction \((\hat{y}_t, \hat{s}_t)\), where \(\hat{y}_t \in \mathbb{R}^K\) is a vector of logits representing class probabilities, and \(\hat{s}_t \in \mathbb{R}^2\) represents the \(x, y\) coordinates of the event within the frame.
-The final class \(c_t\) is obtained by applying argmax to \(\hat{y}_t\), ensuring frame-level precision for each event.
+    \item \textbf{Capturing Local Spatio-Temporal Features}: The model must be able to detect subtle visual changes and movements across adjacent frames, which is crucial for differentiating between events that may look quite similar.
+    \item \textbf{Incorporating Long-Term Temporal Context}: By analyzing a wider temporal range, the model can better understand how events unfold over time, such as tracking how player movements or actions develop before and after a key moment.
+    \item \textbf{Producing Dense Frame-Level Predictions}: For each frame \(x_t\), the model outputs predictions \((\hat{y}_t, \hat{s}_t)\), where \(\hat{y}_t \in \mathbb{R}^K\) represents the class probabilities in a vector of logits, and \(\hat{s}_t \in \mathbb{R}^2\) provides the spatial coordinates \((x, y)\) of the event in the frame.
+The event class \(c_t\) is determined by applying argmax to \(\hat{y}_t\), ensuring accuracy at the frame level for each event.
 \end{itemize}
 
-These requirements call for a robust and end-to-end trainable architecture capable of leveraging both temporal and spatial information.
-Our approach utilizes a sequence model that integrates local spatial-temporal features.
+Meeting these requirements necessitates a robust, end-to-end architecture that effectively leverages both spatial and temporal data.
+Our approach employs a sequence model that integrates local spatio-temporal features to achieve this goal.
 
@@
 
-\section{EXPERIMENTS}
-\label{sec:experiments}
+\section{Experiments}
 \subsection{Implementation Details}

### 2024-10-31 paper.tex
refine section titles and enhance model architecture description for clarity

@@
 
-\subsection{Precise Event Spotting (PES)}
+\subsection{Precise Event Spotting}
 
@@
 \subsection{Model Architecture}
+To effectively learn spatio-temporal features, we propose a multi-task deep learning model comprising three key components: a Feature Extractor, a Dual-attention Feature Aggregation module, and Spatio-Temporal Prediction Heads.
+Drawing inspiration from Hong et al.\cite{spot22}, our model employs a RegNet-Y backbone \cite{radosavovic2020designingnetworkdesignspaces} with GSM \cite{9156729} for adaptive temporal shifts to extract features from each input frame.
+These features are subsequently aggregated via a dual-attention mechanism, integrating spatial and temporal information to enhance feature representations.
+The model then predicts event classes and spatial coordinates through distinct heads, each optimized with a multi-task loss function that balances temporal and spatial prediction objectives.
+
+\begin{figure}[htbp]
+    \centerline{\includegraphics{fig1.png}}
+    \caption{Example of a figure caption.}
+    \label{fig}
+    \end{figure}
 \subsubsection{Feature Extractor}
-\subsubsection{Temporal Event Detection}
-\subsubsection{Spatial Event Detection}
-\subsubsection{Multi-Task Learning}
-\subsubsection{Loss Function}
+The Feature Extractor processes each frame \( x_t \in \mathbb{R}^{H \times W \times 3} \) using a RegNet-Y backbone combined directly with a Gate Shift Module (GSM) to capture spatial and temporal information simultaneously.
+By embedding GSM within RegNet-Y, the network learns not only spatial structures but also the temporal motion present across frames, as GSM shifts features adaptively to track long-term dependencies.
+This integration produces a spatio-temporal feature \( f_t \in \mathbb{R}^d \) that captures both motion and spatial details, equipping the model to accurately interpret the flow of events and predict their progression.
+
+\subsubsection{Dual-attention Feature Aggregation}
+\begin{itemize}
+    % TODO: Review the original Squeeze and Excitation paper, to check if the explanation is correct. Also, add citation
+    \item \textbf{Channel Attention Module:} The Channel Attention Module employs a Squeeze-and-Excitation mechanism to refine feature representation by emphasizing informative channels.
+This allows the model to focus on key spatial features within each frame, enhancing its sensitivity to subtle visual cues and spatial patterns.
+By directing attention to relevant regions, the module aids the model in distinguishing between visually similar events occurring in different locations, improving accuracy in event differentiation.
+
+    % TODO: Review the original Transformer paper, to check if the explanation is correct. Also, add citation
+    \item \textbf{Temporal Attention Module:} Utilizing multi-head attention as described in the *Attention is All You Need* paper, the Temporal Attention Module aggregates features across adjacent frames to capture long-term dependencies and evolving event dynamics.
+By focusing on relevant temporal patterns within a broader context, this module enables the model to anticipate the timing and progression of key events with greater accuracy.
+
+\end{itemize}
+\subsubsection{Spatio-Temporal Prediction Heads}
+The model predicts event classes and spatial coordinates through distinct heads, each optimized with a multi-task loss function that balances temporal and spatial prediction objectives.
+The event class head outputs a vector of logits \(\hat{y}_t\) representing the predicted class probabilities for each event, while the spatial head outputs a vector of coordinates \(\hat{s}_t\) representing the predicted spatial location of the event within the frame.
+By jointly optimizing these heads, the model can effectively learn spatio-temporal features and produce accurate predictions for both event timing and location.
+\subsubsection{Multi-task Loss Function}
+The model is trained with a multi-task loss function that balances temporal and spatial prediction objectives, ensuring that the model learns to predict both when and where key events occur.
+The loss function is defined as the sum of two terms: a temporal classification loss and a spatial regression loss.
+The temporal classification loss penalizes errors in event class predictions
 

### 2024-10-31 paper.tex
refine model architecture description and add TODOs for future enhancements

@@
 
+% TODO: Add a Math formula for the model architecture: ...
+
 \begin{figure}[htbp]
@@
 \subsubsection{Spatio-Temporal Prediction Heads}
+% TODO: Refine this 
 The model predicts event classes and spatial coordinates through distinct heads, each optimized with a multi-task loss function that balances temporal and spatial prediction objectives.

### 2024-11-01 paper.tex
refined "Dual Attention Block"

@@
 \title{Multi-Task Temporal and Spatial Networks for Precise Event Spotting in Volleyball Videos\\
-\thanks{Identify applicable funding agency here. If none, delete this.}
+% \thanks{Identify applicable funding agency here. If none, delete this.}
 }
@@
 Our best model achieves a combined mAP of 85.46 across various temporal and spatial thresholds.
-Notably, we find that incorporating spatial predictions enhances temporal mAP by 5.89 points, underscoring the synergy between spatial and temporal analysis.
+    % TODO: This part should compare results of SPOT and TDEED on KOVO
+    %  Notably, we find that incorporating spatial predictions enhances temporal mAP by 5.89 points, underscoring the synergy between spatial and temporal analysis. 
      To the best of our knowledge, this is the first work addressing this task, establishing a strong baseline for future research in spatio-temporal event spotting.
@@
     \item \textbf{Model Development:} We propose a multi-task deep learning model that jointly predicts event timing and spatial positions, leveraging this dual focus to achieve improved performance. 
-Notably, incorporating spatial predictions into our model enhances temporal mAP by 5.89 points.
+    % Notably, incorporating spatial predictions into our model enhances temporal mAP by 5.89 points.
 \end{itemize}
@@
     \item \textbf{Producing Dense Frame-Level Predictions}: For each frame \(x_t\), the model outputs predictions \((\hat{y}_t, \hat{s}_t)\), where \(\hat{y}_t \in \mathbb{R}^K\) represents the class probabilities in a vector of logits, and \(\hat{s}_t \in \mathbb{R}^2\) provides the spatial coordinates \((x, y)\) of the event in the frame.
-The event class \(c_t\) is determined by applying argmax to \(\hat{y}_t\), ensuring accuracy at the frame level for each event.
+The event class \(c_t\) is then determined by applying argmax to \(\hat{y}_t\).
 \end{itemize}
@@
     \centerline{\includegraphics{fig1.png}}
-    \caption{Example of a figure caption.}
+    \caption{Model architecture.}
     \label{fig}
@@
 
-\subsubsection{Dual-attention Feature Aggregation}
+\subsubsection{Dual-Attention Feature Aggregation}
+The Dual-Attention Feature Aggregation is a layered structure that combines both spatial and temporal attention to enhance the model's ability to identify complex event dynamics.
+By integrating a Channel Attention Module and a Temporal Attention Module within each dual-attention layer, this approach enables the model to focus on the most informative features across both spatial and temporal dimensions.
+Rather than treating each frame equally, the dual-attention mechanism selectively emphasizes frames and features that are most relevant for classification, allowing the model to capture critical moments and transitions accurately, which is especially valuable in fast-paced scenarios.
+
+\begin{figure}[htbp]
+    \centerline{\includegraphics{fig1.png}}
+    \caption{Dual-Attention Feature Aggregation Block.}
+    \label{fig2}
+    \end{figure}
+
 \begin{itemize}
-    % TODO: Review the original Squeeze and Excitation paper, to check if the explanation is correct. Also, add citation
-    \item \textbf{Channel Attention Module:} The Channel Attention Module employs a Squeeze-and-Excitation mechanism to refine feature representation by emphasizing informative channels.
-This allows the model to focus on key spatial features within each frame, enhancing its sensitivity to subtle visual cues and spatial patterns.
-By directing attention to relevant regions, the module aids the model in distinguishing between visually similar events occurring in different locations, improving accuracy in event differentiation.
+    \item \textbf{Channel Attention Module:} This module employs the Squeeze-and-Excitation (SE) mechanism \cite{8578843} to recalibrate features on a channel level, highlighting the most informative channels within each frame.
+By directing attention to key spatial regions, it helps the model differentiate visually similar frames.
+In fast-paced sports like volleyball, this allows the model to distinguish subtle differences, such as the initiation of a spike versus a feint or a quick switch from blocking to defensive stance, which may look alike but indicate different actions.
 
-    % TODO: Review the original Transformer paper, to check if the explanation is correct. Also, add citation
-    \item \textbf{Temporal Attention Module:} Utilizing multi-head attention as described in the *Attention is All You Need* paper, the Temporal Attention Module aggregates features across adjacent frames to capture long-term dependencies and evolving event dynamics.
-By focusing on relevant temporal patterns within a broader context, this module enables the model to anticipate the timing and progression of key events with greater accuracy.
+    \item \textbf{Temporal Attention Module:} This encoder-only module applies multi-head attention \cite{10.5555/3295222.3295349} across frames to capture long-term dependencies and the progression of events.
+By selectively focusing on frames that contribute most to classification rather than treating all frames equally, the Temporal Attention Module enhances the model's ability to identify key moments, accurately interpreting event timing and dynamics in high-speed sequences.
+\end{itemize}
 
-\end{itemize}
 \subsubsection{Spatio-Temporal Prediction Heads}

### 2024-11-01 paper.tex
added predct head, loss func, author list

@@
 \and
-\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
+\IEEEauthorblockN{2\textsuperscript{nd} Ankhzaya Jamsrandorj}
+\IEEEauthorblockA{\textit{Human Computer Interface and Robotics} \\
+\textit{University of Science and Technology}\\
+Daejeon, 34113, Republic of Korea \\
+ankhaa@ust.ac.kr}
+\and
+\IEEEauthorblockN{3\textsuperscript{rd} Vanyi Chao}
+\IEEEauthorblockA{\textit{AI Robotics} \\
+\textit{University of Science and Technology}\\
+Daejeon, 34113, Republic of Korea \\
+vanyi@ust.ac.kr}
+\and
+\IEEEauthorblockN{4\textsuperscript{th} Yin May Oo}
+\IEEEauthorblockA{\textit{AI Robotics} \\
+\textit{University of Science and Technology}\\
+Daejeon, 34113, Republic of Korea \\
+yinmay@ust.ac.kr}
+\and
+\IEEEauthorblockN{5\textsuperscript{th} Kyung-Ryoul Mun}
+\IEEEauthorblockA{\textit{Center for Artificial Intelligence} \\
+\textit{Korea Institute of Science and Technology}\\
+Seoul, 02792, Republic of Korea \\
+krmoon02@kist.re.kr}
+\and
+\IEEEauthorblockN{6\textsuperscript{th} Jinwook Kim}
+\IEEEauthorblockA{\textit{Center for Artificial Intelligence} \\
+\textit{Korea Institute of Science and Technology}\\
 City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
+jinwook.kim21@gmail.com}
 }
@@
     In sport videos analysis, especially in speedy sports such as Volleyball, understanding and localizing the precise timing and location of actions and events are critical.
-We introduce a new task: precise spatio-temporal event spotting, which aims to detect both when and where key events happen.
+We introduce a new task: Precise Spatio-Temporal Event Spotting, which aims to detect both when and where key events happen.
 To support this, we develop the KOVO Volleyball Event Dataset, featuring 947 rally videos, and 5,935 events, annotated for both temporal and spatial localization.
@@
 Among these, \textit{Video Classification} aims to assign a single label to an entire video, providing a broad understanding of the content but often lacking frame-level precision.
-In contrast, \textit{Temporal Action Localization (TAL)} focuses on identifying time intervals where specific actions occur within untrimmed videos.
-Complementing these is \textit{Precise Action Spotting (PES)}, which identifies the precise frames that capture key events, requiring models to discern subtle temporal differences and distinguish visually similar frames \cite{spot22}.
+In contrast, \textit{Temporal Action Localization (TAL)} centers on pinpointing time intervals where specific actions take place within untrimmed videos.
+Complementing TAL, \textit{Precise Action Spotting (PES)} seeks to identify the exact frames that capture crucial events, requiring models to recognize subtle temporal distinctions and discern visually similar frames \cite{spot22}.
 
-Recent advancements in action spotting, such as \textit{T-DEED} \cite{tdeed23} and \textit{E2E-Spot} \cite{spot22}, have demonstrated the ability of models to achieve frame-level precision in fast-paced events using deep learning architectures.
-Datasets like \textit{FigureSkating} \cite{figureskating} and \textit{FineDiving} \cite{finediving} have been pivotal in advancing action spotting, emphasizing the importance of precise temporal detection in sports with individual athletes.
-However, these datasets are tailored to specific sports and do not capture the complexity and rapid dynamics of team-based, high-speed sports, such as volleyball.
+Recent developments in action spotting, like \textit{T-DEED} \cite{tdeed23} and \textit{E2E-Spot} \cite{spot22}, have shown that models can achieve frame-level accuracy in capturing fast-paced events by leveraging deep learning architectures.
+Datasets such as \textit{FigureSkating} \cite{figureskating} and \textit{FineDiving} \cite{finediving} have driven progress in action spotting, particularly highlighting the need for precise temporal detection in sports focused on individual athletes.
+However, these datasets are narrowly focused on specific sports and do not reflect the rapid interactions and complexities seen in high-speed, team-oriented sports like volleyball.
 
-In volleyball, rapid play transitions occur within specific areas of the court, making precise spatial localization as important as temporal accuracy.
-To address this, we introduce the new task of \textit{Precise spatio-temporal event spotting}, designed to detect both the exact timing and spatial location of key events.
-Unlike conventional action spotting, this task provides richer insights into player positioning and movement patterns, which are crucial for analyzing volleyball gameplay.
+In volleyball, quick transitions play out in particular regions of the court, making spatial localization just as critical as temporal precision.
+To address this gap, we introduce a new task: \textit{Precise Spatio-Temporal Event Spotting}, which targets both the exact timing and spatial positioning of key events.
+This approach, unlike traditional action spotting, aims to provide deeper insights into player positioning and movement patterns, which are essential for analyzing volleyball gameplay.
 
-In other sports, datasets like \textit{SoccerNet-v2} \cite{soccernetv2} have pushed the boundaries of action spotting through rich temporal and spatial annotations, significantly advancing model capabilities.
-Yet, no equivalent dataset exists for volleyball, a sport characterized by its rapid exchanges and the need for precise localization of actions.
-To fill this gap, we introduce the \textit{KOVO Event Dataset}, comprising 947 rally videos, 890,797 frames, and 5,935 annotated key actions.
-This dataset offers granular annotations for both temporal and spatial event localization, making it a valuable resource for developing models that capture the intricacies of volleyball.
+For other sports, datasets like \textit{SoccerNet-v2} \cite{soccernetv2} have advanced action spotting with detailed temporal and spatial annotations, helping push model capabilities forward.
+Yet, no similar dataset exists for volleyball, a sport characterized by its rapid exchanges and high demand for spatial precision.
+To bridge this gap, we present the \textit{KOVO Event Dataset}, which consists of 947 rally videos, 890,797 frames, and 5,935 annotated key actions.
+This dataset provides fine-grained annotations for both temporal and spatial event localization, making it an invaluable resource for building models that capture volleyball's unique dynamics.
 
@@
 \begin{itemize}
-    \item \textbf{New Task Introduction:} We introduce the task of Precise spatio-temporal event spotting, specifically tailored for the dynamics of volleyball.
-    \item \textbf{Dataset Development:} We present the \textit{KOVO Event Dataset}, the first of its kind to include detailed temporal and spatial annotations for volleyball rallies, aimed at fostering research in this area.
-    \item \textbf{Model Development:} We propose a multi-task deep learning model that jointly predicts event timing and spatial positions, leveraging this dual focus to achieve improved performance. 
+    \item \textbf{New Task Introduction:} We define the task of Precise Spatio-Temporal Event Spotting, tailored specifically to capture the rapid dynamics of volleyball.
+    \item \textbf{Dataset Development:} We introduce the \textit{KOVO Event Dataset}, the first dataset to feature detailed temporal and spatial annotations for volleyball rallies, intended to drive research in this domain.
+    \item \textbf{Model Development:} We propose a multi-task deep learning model that jointly predicts event timing and spatial locations, using this dual focus to achieve better performance.
     % Notably, incorporating spatial predictions into our model enhances temporal mAP by 5.89 points.
@@
 Our best model achieves a temporal mAP of 90.59, a spatial mAP of 77.94, and a combined mAP of 85.46, providing a strong baseline for this new task.
-As far as we are aware, this work is the first to explore Precise spatio-temporal event spotting in volleyball, setting the stage for future research in this area.
+To the best of our knowledge, this work is the first to explore Precise Spatio-Temporal Event Spotting in volleyball, paving the way for future research in this field.
 
@@
 Understanding event locations is key to analyzing player movements and strategies.
-Our work addresses this by introducing a new task and dataset for Precise spatio-temporal event spotting in volleyball, capturing both event timing and location.
+Our work addresses this by introducing a new task and dataset for Precise Spatio-Temporal Event Spotting in volleyball, capturing both event timing and location.
 
@@
 To effectively learn spatio-temporal features, we propose a multi-task deep learning model comprising three key components: a Feature Extractor, a Dual-attention Feature Aggregation module, and Spatio-Temporal Prediction Heads.
-Drawing inspiration from Hong et al.\cite{spot22}, our model employs a RegNet-Y backbone \cite{radosavovic2020designingnetworkdesignspaces} with GSM \cite{9156729} for adaptive temporal shifts to extract features from each input frame.
-These features are subsequently aggregated via a dual-attention mechanism, integrating spatial and temporal information to enhance feature representations.
-The model then predicts event classes and spatial coordinates through distinct heads, each optimized with a multi-task loss function that balances temporal and spatial prediction objectives.
+Drawing inspiration from Hong et al.\cite{spot22}, our model utilizes a RegNet-Y backbone \cite{radosavovic2020designingnetworkdesignspaces} combined with a Gate Shift Module (GSM) \cite{9156729} to adaptively shift temporal features for each input frame.
+These features are then aggregated through a dual-attention mechanism that merges spatial and temporal information, enhancing the representation of features.
+The model outputs event classifications and spatial coordinates using separate heads, each trained with a multi-task loss function that balances both temporal and spatial prediction goals.
 
@@
 \end{figure}
+
 \subsubsection{Feature Extractor}
-The Feature Extractor processes each frame \( x_t \in \mathbb{R}^{H \times W \times 3} \) using a RegNet-Y backbone combined directly with a Gate Shift Module (GSM) to capture spatial and temporal information simultaneously.
-By embedding GSM within RegNet-Y, the network learns not only spatial structures but also the temporal motion present across frames, as GSM shifts features adaptively to track long-term dependencies.
-This integration produces a spatio-temporal feature \( f_t \in \mathbb{R}^d \) that captures both motion and spatial details, equipping the model to accurately interpret the flow of events and predict their progression.
+The Feature Extractor processes each frame \( x_t \in \mathbb{R}^{H \times W \times 3} \) using a RegNet-Y backbone integrated with a Gate Shift Module (GSM) to capture both spatial and temporal information at once.
+With GSM embedded in RegNet-Y, the network learns not only spatial details but also temporal motion between frames, as GSM adaptively shifts features to track longer-term dependencies.
+This integration produces a spatio-temporal feature \( f_t \in \mathbb{R}^d \) that captures both motion and spatial characteristics, equipping the model to interpret event flow and predict its progression accurately.
 
 \subsubsection{Dual-Attention Feature Aggregation}
-The Dual-Attention Feature Aggregation is a layered structure that combines both spatial and temporal attention to enhance the model's ability to identify complex event dynamics.
-By integrating a Channel Attention Module and a Temporal Attention Module within each dual-attention layer, this approach enables the model to focus on the most informative features across both spatial and temporal dimensions.
-Rather than treating each frame equally, the dual-attention mechanism selectively emphasizes frames and features that are most relevant for classification, allowing the model to capture critical moments and transitions accurately, which is especially valuable in fast-paced scenarios.
+The Dual-Attention Feature Aggregation consists of layers combining spatial and temporal attention to improve the model’s recognition of complex event dynamics.
+By integrating a Channel Attention Module and a Temporal Attention Module within each layer, this setup enables the model to emphasize the most informative spatial and temporal features.
+The dual-attention mechanism selectively focuses on frames and features essential for classification, allowing the model to capture critical moments and transitions precisely, which is especially important in fast-paced scenarios.
 
@@
 \begin{itemize}
-    \item \textbf{Channel Attention Module:} This module employs the Squeeze-and-Excitation (SE) mechanism \cite{8578843} to recalibrate features on a channel level, highlighting the most informative channels within each frame.
-By directing attention to key spatial regions, it helps the model differentiate visually similar frames.
-In fast-paced sports like volleyball, this allows the model to distinguish subtle differences, such as the initiation of a spike versus a feint or a quick switch from blocking to defensive stance, which may look alike but indicate different actions.
+    \item \textbf{Channel Attention Module:} This module uses the Squeeze-and-Excitation (SE) mechanism \cite{8578843} for channel-level recalibration, bringing forward the most informative channels within each frame.
+By focusing on key spatial regions, it helps the model differentiate visually similar frames.
+In fast-paced sports like volleyball, this allows the model to recognize subtle differences, such as distinguishing a spike attempt from a feint or a quick switch from blocking to defensive posture, which may look alike but signify different actions.
 
-    \item \textbf{Temporal Attention Module:} This encoder-only module applies multi-head attention \cite{10.5555/3295222.3295349} across frames to capture long-term dependencies and the progression of events.
-By selectively focusing on frames that contribute most to classification rather than treating all frames equally, the Temporal Attention Module enhances the model's ability to identify key moments, accurately interpreting event timing and dynamics in high-speed sequences.
+    \item \textbf{Temporal Attention Module:} This encoder-only module uses multi-head attention \cite{10.5555/3295222.3295349} across frames to capture dependencies over time and the flow of events.
+By selectively focusing on frames that most contribute to classification, rather than treating all frames equally, the Temporal Attention Module enhances the model’s ability to pinpoint key moments and accurately understand event timing and dynamics in fast-paced sequences.
 \end{itemize}
@@
 \subsubsection{Spatio-Temporal Prediction Heads}
-% TODO: Refine this 
-The model predicts event classes and spatial coordinates through distinct heads, each optimized with a multi-task loss function that balances temporal and spatial prediction objectives.
-The event class head outputs a vector of logits \(\hat{y}_t\) representing the predicted class probabilities for each event, while the spatial head outputs a vector of coordinates \(\hat{s}_t\) representing the predicted spatial location of the event within the frame.
-By jointly optimizing these heads, the model can effectively learn spatio-temporal features and produce accurate predictions for both event timing and location.
+
+After the Dual-Attention Aggregation Block, the features are passed into two separate prediction heads in parallel: one for predicting the spatial location of events and the other for identifying event classes.
+Each head is optimized with a multi-task loss function to balance both temporal and spatial prediction objectives effectively.
+
+\begin{itemize}
+    \item \textbf{Event Class Head:} This head outputs a vector of classification logits \(\hat{y}_t\), which represents the probabilities for each possible event class.
+The predicted event class \(\hat{C}\) is obtained by applying the \(\arg\max\) function:
+    \[
+    \hat{C} = \arg\max(\hat{y}_t)
+    \]
+
+    \item \textbf{Spatial Location Head:} This head outputs logits for the spatial location of the event, represented as coordinates \(\hat{s}_t\).
+To obtain a normalized value between 0 and 1, a sigmoid function is applied to the location logits, resulting in the spatial location \(\hat{L}\):
+    \[
+    \hat{L} = \sigma(\hat{s}_t)
+    \]
+    where \(\sigma\) denotes the sigmoid function, ensuring that \(\hat{L}\) is expressed as a proportion of the frame dimensions.
+\end{itemize}
+
 \subsubsection{Multi-task Loss Function}
-The model is trained with a multi-task loss function that balances temporal and spatial prediction objectives, ensuring that the model learns to predict both when and where key events occur.
-The loss function is defined as the sum of two terms: a temporal classification loss and a spatial regression loss.
-The temporal classification loss penalizes errors in event class predictions
+
+The model is trained using a multi-task loss function to balance the objectives of temporal event classification and spatial location prediction, enabling the model to learn both when and where key events occur.
+The total loss is the sum of two components: a temporal classification loss for event class predictions and a spatial regression loss for location accuracy.
+These are defined as follows:
+
+\begin{itemize}
+    \item \textbf{Temporal Classification Loss (Cross-Entropy):} The event class prediction is supervised with a cross-entropy loss, \(\mathcal{L}_{\text{class}}\), which includes an additional background class (class 0) for non-event frames.
+Due to the sparsity of event frames relative to background frames, a weighting strategy is applied to emphasize event frames more heavily during training.
+Following the approach in \textit{E2E-Spot} \cite{spot22}, we assign a weight of 5 to event classes and a weight of 1 to the background class.
+The weighted cross-entropy loss is defined as:
+    \[
+    \mathcal{L}_{\text{class}} = -\sum_{c} w_c \, y_{c} \, \log(\hat{y}_{c})
+    \]
+    where \(w_c\) is the class weight (5 for event classes, 1 for the background), \(y_c\) is the ground-truth label, and \(\hat{y}_{c}\) is the predicted probability for each class \(c\).
+
+    \item \textbf{Spatial Location Loss (L1):} The spatial prediction is supervised with an L1 loss, \(\mathcal{L}_{\text{spatial}}\), which calculates the absolute difference between the predicted location \(\hat{L}\) and the ground truth location \(L\).
+A binary mask \(M\) is applied to focus the loss on frames where the class label is greater than 0 (i.e., frames containing events), thus avoiding gradient backpropagation of spatial predictions on background frames:
+    \[
+    \mathcal{L}_{\text{spatial}} = \frac{1}{\sum M + \epsilon} \sum_{t} M_t \, |\hat{L}_t - L_t|
+    \]
+    where \(M_t\) is 1 for event frames (class label $y_c > 0$) and 0 for background frames ($y_c = 0$), and \(\epsilon\) is a small constant for numerical stability.
+
+\end{itemize}
+
+The total multi-task loss, combining both the temporal classification and spatial location losses, is defined as:
+\[
+\mathcal{L} = \mathcal{L}_{\text{class}} + \mathcal{L}_{\text{spatial}}
+\]
+
+By jointly optimizing \(\mathcal{L}_{\text{class}}\) and \(\mathcal{L}_{\text{spatial}}\), the model effectively learns spatio-temporal features, enabling accurate predictions of both event timing and spatial location.
 

### 2024-11-01 paper.tex
add drafts for dataset section

@@
 \section{Dataset Overview}
-
+% TODO: Please refine this crappy draft
+We collect games from 23-24 seasons from a private kovo database.
 \subsection{Data Content and Statistics}
+We wrote python script to automatically download volleyball games videos and its event timing.
+Then we use May's field keypoints detection to segmentize each game into replay vs inplay sequences (we call it rallies).
+Then, we extract each short video into indifual frames, at 30 fps and 1280x720.
+To annotate the event locaion, we build our own proprieatry tool, which is described in the anntoation process subsection.
 \subsection{Annotation Process}
+We annotate each event with location.
+For volleyball, the ball location is typically the most important cue for each game event.
+Therefore, most of the time, we annotate the ball location as the event location.
+Also, ball location tracking is a well researched topic. This means that we could use ball detection module such as vanyis to get the ball location without human labour.
+\begin{figure}[htbp]
+    \centerline{\includegraphics{fig1.png}}
+    \caption{The GUI of our internal annotation tool}
+    \label{fig-annotate-app}
+\end{figure}
 \subsection{Dataset Splits}
+We handpicked videos with diverse visual features to ....
+then we split them into train val test ...
 \subsection{Release and Access}
@@
 However, we have made a resized version (512x288 resolution) along with the corresponding annotations available on Kaggle, totaling 100GB.
-The dataset can be accessed at \url{www.kaggle.com/soon}.
+Our dataset is available at our project page: \url{www.kaggle.com/soon}.
+Note that, due to copyright restrictions, please fill in the NDA form to get access to the data.
 

### 2024-11-01 paper.tex
add cite for vanyi and may works

@@
 We wrote python script to automatically download volleyball games videos and its event timing.
-Then we use May's field keypoints detection to segmentize each game into replay vs inplay sequences (we call it rallies).
+Then we use May's field keypoints detection \cite{10312494} to segmentize each game into replay vs inplay sequences (we call it rallies).
 Then, we extract each short video into indifual frames, at 30 fps and 1280x720.
@@
 Therefore, most of the time, we annotate the ball location as the event location.
-Also, ball location tracking is a well researched topic. This means that we could use ball detection module such as vanyis to get the ball location without human labour.
+Also, ball location tracking is a well researched topic. This means that we could use ball detection module such as vanyis \cite{10312079} to get the ball location without human labour.
 \begin{figure}[htbp]

### 2024-11-01 paper.tex
add tables for kovo dataset stats

@@
 \subsection{Data Content and Statistics}
+
 We wrote python script to automatically download volleyball games videos and its event timing.
@@
 Also, ball location tracking is a well researched topic. This means that we could use ball detection module such as vanyis \cite{10312079} to get the ball location without human labour.
+\begin{table}[htbp]
+    \caption{KOVO Dataset Action Counts and Percentages}
+    \begin{center}
+    \begin{tabular}{|c|c|c|}
+    \hline
+    \textbf{Action} & \textbf{\# Events} & \textbf{Percentage (\%)} \\
+    \hline
+    Serve & 947 & 15.96 \\
+    Receive & 844 & 14.22 \\
+    Set & 1359 & 22.90 \\
+    Spike & 1315 & 22.16 \\
+    Dig & 807 & 13.60 \\
+    Block & 663 & 11.17 \\
+    \hline
+    \end{tabular}
+    \label{tab-kovo-stat1}
+    \end{center}
+    \end{table}
+
 \begin{figure}[htbp]
@@
 \end{figure}
+
 \subsection{Dataset Splits}
@@
 then we split them into train val test ...
+
+\begin{table}[htbp]
+    \caption{Dataset Splits for Volleyball Analysis}
+    \begin{center}
+    \begin{tabular}{|c|c|c|c|}
+    \hline
+    \textbf{Split} & \textbf{\# Clips (Rallies)} & \textbf{\# Events} & \textbf{\# Frames} \\
+    \hline
+    All & 947 & 5,935 & 257,388 \\
+    Train & 561 & 3,631 & 156,818 \\
+    Validation & 220 & 1,356 & 58,430 \\
+    Test & 166 & 948 & 42,140 \\
+    \hline
+    \end{tabular}
+    \label{tab-kovo-split}
+    \end{center}
+    \end{table}
 \subsection{Release and Access}

### 2024-11-01 paper.tex
added city country for dr kim
done dataset sec

@@
 
-\title{Multi-Task Temporal and Spatial Networks for Precise Event Spotting in Volleyball Videos\\
+\title{Dual-Attention Network for Precise Temporal and Spatial Event Spotting in Volleyball Videos\\
 % \thanks{Identify applicable funding agency here. If none, delete this.}
@@
 \textit{Korea Institute of Science and Technology}\\
-City, Country \\
+Seoul, 02792, Republic of Korea \\
 jinwook.kim21@gmail.com}
@@
 
-\section{Dataset Overview}
-% TODO: Please refine this crappy draft
-We collect games from 23-24 seasons from a private kovo database.
-\subsection{Data Content and Statistics}
+\section{Dataset Overview} With permission from the Korea Volleyball Federation (KOVO) \cite{kovoweb}, we collected 235 volleyball game videos, each containing temporal annotations for game events.
+Using field keypoint detection \cite{10312494}, we segmented each game into "replay" and "in-play" sequences (rallies).
+Each rally was then converted to individual frames at 1280x720 resolution and 30 fps.
+To facilitate event location annotation, we developed a proprietary tool, further detailed in the Annotation Process subsection.
 
-We wrote python script to automatically download volleyball games videos and its event timing.
-Then we use May's field keypoints detection \cite{10312494} to segmentize each game into replay vs inplay sequences (we call it rallies).
-Then, we extract each short video into indifual frames, at 30 fps and 1280x720.
-To annotate the event locaion, we build our own proprieatry tool, which is described in the anntoation process subsection.
+% \subsection{Data Content and Statistics} To automate data collection, we created a Python script to download game videos and event timings.
+This data, once segmented into rallies and converted to frames, was annotated using our custom tool, designed to streamline collaboration and expedite labeling.
+Further details on this process are outlined in the Annotation Process subsection.
+
 \subsection{Annotation Process}
-We annotate each event with location.
-For volleyball, the ball location is typically the most important cue for each game event.
-Therefore, most of the time, we annotate the ball location as the event location.
-Also, ball location tracking is a well researched topic. This means that we could use ball detection module such as vanyis \cite{10312079} to get the ball location without human labour.
+
+Each event in the dataset is annotated with precise spatial information, specifically focusing on the ball’s location, as this serves as the primary indicator for volleyball actions.
+To achieve high accuracy, we manually labeled the ball’s position in each frame, ensuring detailed and reliable annotations essential for understanding the dynamics of each event.
+Although this approach is time-intensive, it provides high-quality data that underpins robust event detection and tracking.
+
+The dataset encompasses six core volleyball actions—Serve, Receive, Set, Spike, Dig, and Block—provided by the Korea Volleyball Federation (KOVO).
+These actions capture the key elements of gameplay and balance both offensive and defensive actions critical to rally sequences.
+
+To streamline future work, advanced models like MaxVit Sequential \cite{10.1145/3689061.3689075} could assist in automating the ball-tracking process, reducing manual effort while maintaining annotation quality.
+
 \begin{table}[htbp]
@@
 
-\begin{figure}[htbp]
-    \centerline{\includegraphics{fig1.png}}
-    \caption{The GUI of our internal annotation tool}
-    \label{fig-annotate-app}
-\end{figure}
+    \subsection{Dataset Splits}
 
-\subsection{Dataset Splits}
-We handpicked videos with diverse visual features to ....
-then we split them into train val test ...
+    We divided the KOVO Event Dataset into three distinct subsets: training, validation, and testing.
+These subsets were selected to reflect a balanced representation of rally variations, camera angles, and visual characteristics across different matches, which helps improve model generalization.
+
+    The split ratios are as follows: the training set comprises 561 rallies (approximately 60\% of the dataset), the validation set includes 220 rallies (around 23\%), and the testing set contains 166 rallies (about 17.5\%).
 
@@
 \end{table}
+
 \subsection{Release and Access}
-Given the large size of the dataset, we are unable to release the full-resolution (1280x720) videos in this paper.
-However, we have made a resized version (512x288 resolution) along with the corresponding annotations available on Kaggle, totaling 100GB.
-Our dataset is available at our project page: \url{www.kaggle.com/soon}.
-Note that, due to copyright restrictions, please fill in the NDA form to get access to the data.
+
+The full-resolution dataset is unavailable due to size constraints, but a resized version (512x288) with annotations (100GB) is accessible on Kaggle at \url{www.kaggle.com/soon}.
+Access requires a completed NDA form due to copyright restrictions.
 

### 2024-11-01 paper.tex
refined title
added figure for kovo dataset

@@
 
-\title{Dual-Attention Network for Precise Temporal and Spatial Event Spotting in Volleyball Videos\\
+\title{DMTN: Dual-Attention Multi-Task Network for Precise Spatio-Temporal Event Spotting in Volleyball Videos\\
 % \thanks{Identify applicable funding agency here. If none, delete this.}
@@
 In volleyball, quick transitions play out in particular regions of the court, making spatial localization just as critical as temporal precision.
-To address this gap, we introduce a new task: \textit{Precise Spatio-Temporal Event Spotting}, which targets both the exact timing and spatial positioning of key events.
+To address this gap, we introduce a new task: \textit{Precise Spatio-Temporal Event Spotting} (as depicted in Fig.~\ref{fig-kovo-ex}), which targets both the exact timing and spatial positioning of key events.
 This approach, unlike traditional action spotting, aims to provide deeper insights into player positioning and movement patterns, which are essential for analyzing volleyball gameplay.
@@
 This dataset provides fine-grained annotations for both temporal and spatial event localization, making it an invaluable resource for building models that capture volleyball's unique dynamics.
+
+\begin{figure*}[t] 
+    \centering
+    \includegraphics[width=\textwidth]{figures/fig-kovo-ex.jpg}
+    \caption{Example sequence for a spike event, highlighting the exact timing (\(t+3\)) with the spatial location annotated by the white circle and the event class indicated by the text above it.}
+    \label{fig-kovo-ex}
+\end{figure*}
 
@@
 \begin{figure}[htbp]
-    \centerline{\includegraphics{fig1.png}}
+    \centerline{\includegraphics{figures/fig1.png}}
     \caption{Model architecture.}
@@
 \begin{figure}[htbp]
-    \centerline{\includegraphics{fig1.png}}
+    \centerline{\includegraphics{figures/fig1.png}}
     \caption{Dual-Attention Feature Aggregation Block.}

### 2024-11-01 paper.tex
add fig for model arch [30% complete]
full model arch diagram

@@
 \section{Related work}
-
+% TODO: Can write about Squeeze Ex and Multihead attention and their use in video understanding instead of TAL, etc... (or at least shorten them)
 \subsection{Video Classification}
@@
 
-\begin{figure}[htbp]
-    \centerline{\includegraphics{figures/fig1.png}}
-    \caption{Model architecture.}
-    \label{fig}
-\end{figure}
+\begin{figure*} 
+    \centering
+    \includegraphics[width=\textwidth]{figures/fig-arch.jpg}
+    \caption{Illustration of DMTN Architecture Comprising Three Key Components: (1) \textbf{Feature Extractor} that processes each frame through RegNet-Y with Gate Shift Modules (GSM) to capture both spatial and temporal information; (2) \textbf{Dual-Attention Feature Aggregator} that combines Channel Attention and Temporal Attention mechanisms to integrate local and global spatio-temporal features, enhancing the model’s ability to capture subtle event dynamics; and (3) \textbf{Multi-Task Prediction Heads} that output per-frame classifications and spatial coordinates, enabling precise spatio-temporal event spotting for volleyball gameplay analysis.}    \label{fig-arch}
+\end{figure*}
 
